|

### 2021-12-13 front-and-back-matter/99-appendices.Rmd
Add PRISMA checklist

@@

(ref:drDemeniaTC-scap) shortcap

@@

(ref:drAdLDL-scap) shortcap

@@

(ref:minFU-cap) __shortcap:__

(ref:minFU-scap) shortcap

@@

<!----------------------------------------------------------------------------->
(ref:cprdMinFu-cap) Estimates from the

(ref:cprdMinFu-scap) shortcap

@@

### Comparison with previous analysis of the Whitehall II cohort {#appendix-ipd-whitehall}

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.

(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort

```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_ad.png"))
```
<!----------------------------------------------------------------------------->

@@

(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.

(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias. Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels

```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```

@@

robvis currently contains templates for the following tools:

* ROB2
* ROBINS-I
* QUADAS-2
* ROB1

@@

<!----------------------------------------------------------------------------->
(ref:robSummary-cap) __shortcap:__

(ref:robSummary-scap) shortcap

@@

<!----------------------------------------------------------------------------->
(ref:robTraffic-cap) __shortcap:__

(ref:robTraffic-scap) shortcap

>>>>

### PRISMA Checklist

\arrayrulecolor{white}

<!----------------------------------------------------------------------------->
(ref:prismaTab-caption) __PRISMA Checklist__

(ref:prismaTab-scaption) PRISMA Checklist

```{r prismaTab-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
\arrayrulecolor{black}

@@

(ref:drDemeniaTC-scap) Dose-response meta-analysis of total cholesterol on all-cause dementia

@@

(ref:drAdLDL-scap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease

@@

(ref:minFU-cap) Diagram illustrating the design of two studies. Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up. In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.

(ref:minFU-scap) Illustration of minimum follow-up period in two study designs

@@

<!----------------------------------------------------------------------------->
(ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group. Events occurring within 10 years of inititating statins were discarded, but the participant-time-at-risk was maintained. No minimum follow-up period was applied in those never taking a statin, due to the difficulties in defining the start date for the follow-up period, as discussed in the text above.

(ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up.

@@

@@

(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias. Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels

(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```

@@

### Templates

`robvis` currently contains templates for the following tools:

* ROB2
* ROBINS-I
* QUADAS-2
* ROB1
* General

### Data expectations

@@

<!----------------------------------------------------------------------------->
(ref:robSummary-cap) Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above. Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.

(ref:robSummary-scap) Example risk-of-bias summary barplot

@@

<!----------------------------------------------------------------------------->
(ref:robTraffic-cap) Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.

(ref:robTraffic-scap) Example risk-of-bias traffic-light plot
